Summary of tumor cell classification with `SingleR` for `r params$library_id`

### 2025-07-24 analyses/cell-type-ewings/template_notebooks/auc-singler-workflow/02-singler-results.Rmd
sort order and make sure at least 2 levels to compare

# get the cell types in both
# these should be tumor normal but sometimes that's not the case
singler_cell_types <- unique(caret_df$singler_tumor_normal) |> as.character()
aucell_cell_types <- unique(caret_df$aucell_annotation) |> as.character()

# only calculate confusion matrix if all cell types are the same
if (all(singler_cell_types == aucell_cell_types)) {
  caret::confusionMatrix(
    table(
      caret_df$aucell_annotation,
      caret_df$singler_tumor_normal
    )
  )
}
```

>>>>

# get the cell types in both
# these should be tumor normal but sometimes that's not the case
singler_cell_types <- unique(caret_df$singler_tumor_normal) |> as.character() |> sort()
aucell_cell_types <- unique(caret_df$aucell_annotation) |> as.character() |> sort()

# only calculate confusion matrix if all cell types are the same
if (all(singler_cell_types == aucell_cell_types) & length(singler_cell_types) > 1) {
  caret::confusionMatrix(
    table(
      caret_df$aucell_annotation,
      caret_df$singler_tumor_normal
    )
  )
}
```
